---
title: "Dataset"
---

>   The dataset that i used was from Tom Slee, who used a data scraping code to gather data from Airbnb's website. I chose data from Airbnb listings in philadelphia that were collected in 2017. [Here](http://tomslee.net/airbnb-data-collection-get-the-data) you can find the datasource. For analysis, I used only listings that either had at least 1 review, as a listing with no reviews could not have a overall satisfaction rating, and those that had a rating of zero, as there were no values from 2 -> 0 on the overall satisfaction rating scale. This resulted in 2465 total listings being accounted for during statistical analysis. 
>   The variables that were available were room type, neighborhood, reviews, overall satisfaction with the stay, and price. I did not analyze room id, host id, accomodation size, bedrooms, and latitude/longitude that were also included in this dataset. 

--- 

>Starting with room type, below is the frequency plot of all room types: entire home, private room and shared room.

```{r}
barplot(table(room_type))
count(room_type)
```

>Next is neighborhood, there were 122 neighborhoods identified in the data:

```{r}
barplot(table(neighborhood))
count(neighborhood)
```

> Now with the total amount of reviews for a single listing/property

```{r}
hist(reviews)
summary(reviews)
```

>And now lastly with the price distribution of the listings

```{r}
hist(price)
summary(price)
```
